Developing a preprint culture in biology

### 2012-10-21 ms.tex
fix typo

\keywords{Publishing; Preprint servers; Green Open Access; arXiv.}

@@

PDP is supported by an Alexander Graham Bell scholarship from the National
Sciences and Engineering Council of Canada. EPW is supported by a CAREER Award
from the National Science Foundation (DEB-0953694). JJA is supported by NSF
DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
scholarship and 25 cents found by a coffee machine.  KR is supported by NSF
DEB-1021553. DG is funded by a Discovery Grand from the National Sciences and
Engineering Council of Canada and by the Canada Research Chair program.

>>>>

\keywords{Publishing; Preprint servers; Green Open Access}

@@

PDP is supported by an Alexander Graham Bell scholarship from the National
Sciences and Engineering Council of Canada. EPW is supported by a CAREER Award
from the National Science Foundation (DEB-0953694). JJA is supported by NSF
DEB-0614166 and NSF DEB-0919018.  TP is supported by a FQRNT-MELS post-doctoral
scholarship and 25 cents found by a coffee machine.  KR is supported by NSF
DEB-1021553. DG is funded by a Discovery Grant from the National Sciences and
Engineering Council of Canada and by the Canada Research Chair program.
